---
title: "Config Notebook"
output: html_notebook
---

```{r}
library(benchmarkme)
library(magrittr)
library(data.table, warn.conflicts = FALSE)
```

## Setting the environment

Initially we setup the environment that we will work. In a contabo VPS we install docker and docker-compose. We setup an Rstudio server and a Shiny server that will help on fast prototyping and sharing while Nginx is used for reverse proxy, properly 
configured for web-socket compatibility (see docker-compose definition and nginx config file). An ssl certificate is configured using certbot while using remotes shiny.semantic **4.0.0** is installed for the particular version.

- The computing node is a Virtual Personalized Server and the OS is Ubuntu 20.04 LTS.

```{r}
get_sys_details()[c("cpu", "ram")]
version$os
```

- Inspecting R environment

```{r}
get_r_version() %>% tail(2)
``` 

## Development environment

We use a multistage build Docker file to build rstudio server with all the required
libraries and on top of this we build shiny server so that they share common libraries. 
Note that, to push in a production environment shiny server docker image 
should be defined using only the libraries actually used (e.g. use **renv**).

- Docker *multistage* build that I use for trying thinks...

```
FROM rocker/verse:latest as mstudio
MAINTAINER "Alexandros Kouretsis" akourets@gmail.com
RUN install2.r --error \
    htmlwidgets \
    stringr \
    yaml \
    profvis \
    thematic \
    ggforce \
    gh \
    globals \
    openintro \
    gapminder \
    RSQLite \
    shiny \
    rmarkdown \
    pagedown \
    blogdown \
    bookdown \
    kableExtra \
    glmnet \
    e1071 \
    lightgbm \
    xgboost \
    text2vec \
    caret \
    shinyWidgets \
    shinycssloaders \
    shinyFeedback \ 
    shinythemes \
    flexdashboard \
    shinydashboard \
    plotly \
    echarts4r \
    waiter
    
RUN Rscript -e \
  "remotes::install_version('shiny.semantic', version = '0.4.0', repos = 'http://cran.us.r-project.org')"

RUN install2.r --error benchmarkme

CMD ["/init"]

FROM mstudio as mshiny
RUN apt-get update && apt-get install -y \
    sudo \
    gdebi-core \
    pandoc \
    pandoc-citeproc \
    libcurl4-gnutls-dev \
    libcairo2-dev \
    libxt-dev \
    wget && wget --no-verbose https://download3.rstudio.org/ubuntu-14.04/x86_64/VERSION -O "version.txt" && \
    VERSION=$(cat version.txt)  && \
    wget --no-verbose "https://download3.rstudio.org/ubuntu-14.04/x86_64/shiny-server-$VERSION-amd64.deb" -O ss-latest.deb && \
    gdebi -n ss-latest.deb && \
    rm -f version.txt ss-latest.deb && \
    . /etc/environment && \
    apt-get clean && rm -rf /var/lib/apt/lists/
COPY ./shiny-server.conf  /etc/shiny-server/shiny-server.conf
EXPOSE 3838
COPY shiny-server.sh /usr/bin/shiny-server.sh
RUN ["chmod", "+x", "/usr/bin/shiny-server.sh"]
CMD ["/usr/bin/shiny-server.sh"]
```

- *docker-compose* configuration:

```
services:
  certbot:
    entrypoint: /bin/sh -c 'trap exit TERM; while :; do certbot renew; sleep 12h &
      wait $${!}; done;'
    image: certbot/certbot
    volumes:
    - /home/Projects/manifolR/data/certbot/conf:/etc/letsencrypt:rw
    - /home/Projects/manifolR/data/certbot/www:/var/www/certbot:rw
  mshiny:
    build:
      context: /home/Projects/manifolR
      target: mshiny
    command:
    - /usr/bin/shiny-server.sh
    ports:
    - published: 3939
      target: 3838
    restart: always
    volumes:
    - /home/Projects/manifolR/data/shiny:/srv/shiny-server:rw
  nginx:
    command: /bin/sh -c 'while :; do sleep 6h & wait $${!}; nginx -s reload; done
      & nginx -g "daemon off;"'
    image: nginx
    ports:
    - published: 80
      target: 80
    - published: 443
      target: 443
    restart: always
    volumes:
    - /home/Projects/manifolR/data/nginx/html:/usr/share/nginx/html:rw
    - /home/Projects/manifolR/data/nginx:/etc/nginx/conf.d:rw
    - /home/Projects/manifolR/data/certbot/conf:/etc/letsencrypt:rw
    - /home/Projects/manifolR/data/certbot/www:/var/www/certbot:rw
  rstudio:
    build:
      context: /home/Projects/manifolR
      target: mstudio
    command:
    - /init
    depends_on:
      mshiny:
        condition: service_started
      nginx:
        condition: service_started
    environment:
      PASSWORD: XXX
      ROOT: "TRUE"
      USER: XXX
    ports:
    - published: 8989
      target: 8787
    restart: always
    volumes:
    - vol_mstudio:/home:rw
    - /home/Projects/manifolR/data/shiny:/srv/shiny-server:rw
version: '3.9'
volumes:
  vol_mstudio: {}
```

- *Nginx* configuration

```
server {

        listen 80;
        server_name aledat.eu;
        
        location / {
                return 301 https://$host$request_uri;
        }
        
        location /.well-known/acme-challenge/ {
                root /var/www/certbot;
        }

}

map $http_upgrade $connection_upgrade {

        default upgrade;
        ''      close;

}

server {

        listen 443 ssl;
        server_name aledat.eu;
        root /usr/share/nginx/html;
        
        location /shiny/ {
          rewrite ^/shiny/(.*)$ /$1 break;
          proxy_pass http://mshiny:3838/;
          proxy_redirect http://mshiny:3838/ $scheme://$http_host/shiny/;
          proxy_http_version 1.1;
          proxy_set_header Upgrade $http_upgrade;
          proxy_set_header Connection $connection_upgrade;
          proxy_read_timeout 20d;
          proxy_buffering off;
        }

        location /rstudio/ {
                rewrite ^/rstudio/(.*)$ /$1 break;
                proxy_pass http://rstudio:8787;
                proxy_redirect http://rstudio:8787/ $scheme://$http_host/rstudio/;
                proxy_http_version 1.1;
                proxy_set_header Upgrade $http_upgrade;
                proxy_set_header Connection $connection_upgrade;
                proxy_read_timeout 20d;
        }
        
        ssl_certificate /etc/letsencrypt/live/aledat.eu/fullchain.pem;
        ssl_certificate_key /etc/letsencrypt/live/aledat.eu/privkey.pem;
        include /etc/letsencrypt/options-ssl-nginx.conf;
        ssl_dhparam /etc/letsencrypt/ssl-dhparams.pem;
        
}

```





